Hazelnut: A Bidirectionally Typed \\ Structure Editor Calculus

### 2016-09-24 implementation.tex
working on #6

\subsection{HZ}
We have developed a simple reference implementation of Hazelnut.
In order to reach a wide audience, we decided to implement HZ in the web browser.
In order to take advantage of a mature implementation of the FRP model, we chose to implement HZ using OCaml\footnote{https://ocaml.org/}, the \texttt{js\_of\_ocaml} compiler and associated libraries \cite{DBLP:conf/ml/Balat06}\footnote{http://ocsigen.org/js\_of\_ocaml/} and the OCaml React library\footnote{http://erratique.ch/software/react}.

>>>>

\subsection{HZ}
We have developed a simple reference implementation, HZ, of Hazelnut.  In
order to reach a wide audience, we decided to implement HZ in the web
browser.  In order to take advantage of a mature implementation of the FRP
model, we chose to implement HZ using
OCaml\footnote{\url{https://ocaml.org/}}, the \texttt{js\_of\_ocaml}
compiler and associated libraries
\cite{DBLP:conf/ml/Balat06}\footnote{\url{http://ocsigen.org/js\_of\_ocaml/}}
and the OCaml React
library\footnote{\url{http://erratique.ch/software/react}}.
